|

### 2019-09-03 appendix/appendix.Rmd
Map changes.

```{r man1, echo=TRUE, warning=FALSE, message=FALSE, error=FALSE, cache=TRUE, out.width='.49\\linewidth', fig.width=4, fig.height=4, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation1}Manipulation checks for intervention 1. The first plot shows the geographical distribution of the treatment condition and the second graph displays the number of TDP app downloads from August 2017 to February 2018.'}
# Map manipulation test -- Intervention 1
mapbr <- get_brmap('City')
gaaux <- filter(ga, phase1 == 1)
gaaux <- select(gaaux, ibge_code7, downl)
gaaux <- rename(gaaux, City = ibge_code7)
gaaux <- unique(gaaux)
gaaux$City <- as.numeric(gaaux$City)
gaaux2 <- impact_evaluation_phase2 %>%
  select(ibge_code7) %>%
  transmute(City = as.numeric(ibge_code7)) %>%
  unique()
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 0
gaaux2 <- data.frame(City = mapbr$City)
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 2
gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads',
                                                  'Not in App'))
mapbr <- join_data(mapbr, gaaux, by = 'City')
pMapDownloadsInt1 <- ggplot() + 
  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.02) +
  scale_fill_manual(values=c( "#E69F00", "#0072B2", "#F0E442")) +
  theme_map()
pMapDownloadsInt1

@@

```{r man2, echo=TRUE, warning=FALSE, message=FALSE, error=FALSE, cache=TRUE, out.width='.49\\linewidth', fig.width=4, fig.height=4, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation2}Manipulation checks for intervention 2. The graphs display the geographical and temporal variation of TDP app downloads from August 2018 to February 2019.'}
## Map manipulation test -- Intervention 2
mapbr <- get_brmap('City')
gaaux <- filter(ga, phase2 == 1)
gaaux <- select(gaaux, ibge_code7, downl)
gaaux <- rename(gaaux, City = ibge_code7)
gaaux <- unique(gaaux)
gaaux$City <- as.numeric(gaaux$City)
gaaux2 <- impact_evaluation_phase2 %>%
  select(ibge_code7) %>%
  transmute(City = as.numeric(ibge_code7)) %>%
  unique()
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 0
gaaux2 <- data.frame(City = mapbr$City)
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 2
gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads',
                                                  'Not in App'))
mapbr <- join_data(mapbr, gaaux, by = 'City')
p1 <- ggplot() + 
  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.02) +
  scale_fill_manual(values=c( "#E69F00", "#0072B2", "#F0E442")) +
  theme_map()
p1

>>>>

```{r man1, echo=TRUE, warning=FALSE, message=FALSE, error=FALSE, cache=TRUE, out.width='.49\\linewidth', fig.width=4, fig.height=4, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation1}Manipulation checks for intervention 1. The first plot shows the geographical distribution of the treatment condition and the second graph displays the number of TDP app downloads from August 2017 to February 2018.'}
# Map manipulation test -- Intervention 1
mapbr <- get_brmap('City')
gaaux <- filter(ga, phase1 == 1)
gaaux <- select(gaaux, ibge_code7, downl)
gaaux <- rename(gaaux, City = ibge_code7)
gaaux <- unique(gaaux)
gaaux$City <- as.numeric(gaaux$City)
gaaux2 <- impact_evaluation_phase1 %>%
  select(ibge_code7) %>%
  transmute(City = as.numeric(ibge_code7)) %>%
  unique()
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 0
gaaux2 <- data.frame(City = mapbr$City)
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 2
gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads',
                                                  'Not in App'))
mapbr <- join_data(mapbr, gaaux, by = 'City')
pMapDownloadsInt1 <- ggplot() + 
  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.01) +
  scale_fill_manual(values=c( "#E69F00", "#0072B2", "#F0E442")) +
  theme_map()
pMapDownloadsInt1

@@

```{r man2, echo=TRUE, warning=FALSE, message=FALSE, error=FALSE, cache=TRUE, out.width='.49\\linewidth', fig.width=4, fig.height=4, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation2}Manipulation checks for intervention 2. The graphs display the geographical and temporal variation of TDP app downloads from August 2018 to February 2019.'}
## Map manipulation test -- Intervention 2
mapbr <- get_brmap('City')
gaaux <- filter(ga, phase2 == 1)
gaaux <- select(gaaux, ibge_code7, downl)
gaaux <- rename(gaaux, City = ibge_code7)
gaaux <- unique(gaaux)
gaaux$City <- as.numeric(gaaux$City)
gaaux2 <- impact_evaluation_phase2 %>%
  select(ibge_code7) %>%
  transmute(City = as.numeric(ibge_code7)) %>%
  unique()
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 0
gaaux2 <- data.frame(City = mapbr$City)
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 2
gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads',
                                                  'Not in App'))
mapbr <- join_data(mapbr, gaaux, by = 'City')
p1 <- ggplot() + 
  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.01) +
  scale_fill_manual(values=c( "#E69F00", "#0072B2", "#F0E442")) +
  theme_map()
p1

### 2019-09-03 article/article.Rmd
Map changes.

## Map GA intervention 1
mapbr <- get_brmap('City')
gaaux <- filter(ga, phase1 == 1)
gaaux <- select(gaaux, ibge_code7, downl)
gaaux <- rename(gaaux, City = ibge_code7)
gaaux <- unique(gaaux)
gaaux$City <- as.numeric(gaaux$City)
gaaux2 <- impact_evaluation_phase2 %>%
  select(ibge_code7) %>%
  transmute(City = as.numeric(ibge_code7)) %>%
  unique()
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 0
gaaux2 <- data.frame(City = mapbr$City)
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 2
gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads', 'Not in App'))
mapbr <- join_data(mapbr, gaaux, by = 'City')
pMapDownloadsInt1 <- ggplot() + 
  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.01) +
  scale_fill_manual(values=c( "#E69F00", "#0072B2", "#F0E442")) +
  theme_map()
pMapDownloadsInt1

>>>>

## Map GA intervention 1
mapbr <- get_brmap('City')
gaaux <- filter(ga, phase1 == 1)
gaaux <- select(gaaux, ibge_code7, downl)
gaaux <- rename(gaaux, City = ibge_code7)
gaaux <- unique(gaaux)
gaaux$City <- as.numeric(gaaux$City)
gaaux2 <- impact_evaluation_phase1 %>%
  select(ibge_code7) %>%
  transmute(City = as.numeric(ibge_code7)) %>%
  unique()
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 0
gaaux2 <- data.frame(City = mapbr$City)
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 2
gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads', 'Not in App'))
mapbr <- join_data(mapbr, gaaux, by = 'City')
pMapDownloadsInt1 <- ggplot() + 
  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.01) +
  scale_fill_manual(values=c( "#E69F00", "#0072B2", "#F0E442")) +
  theme_map()
pMapDownloadsInt1
